%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item[{{\textbullet}}]\small{{#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[3]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1 \cdot \space}{\small #2}& \textit{\small #3} \\
    \end{tabular*}\vspace{-5pt}
}



\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\tiny\textbullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Leland Wu}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{leland.wu4@gmail.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.lelandhwu.github.io} & Mobile : +1-617-721-6476 \\
% \end{tabular*}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\centerline{\Huge Leland Wu}}\\
  \centerline{\href{http://lelandhwu.github.io/}{http://www.lelandhwu.github.io} | leland.wu4@gmail.com | 617-721-6476}
\end{tabular*}\vspace{-10pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tufts University}{Boston, MA}
      {B.S in Computer Science;  Major GPA: 3.63/4.0; Cumulative GPA: 3.70/4.0}{Expected May 2020}\vspace{-8pt}
    \begin{itemize}
      \itemsep-0.3em 
       \fontsize{11pt}{12pt}\selectfont{\setlength\itemindent{0pt} \item \textbf{Relevant Coursework}{\small: Data Structures, Discrete Mathematics, Machine Structure and Assembly Language Programming, Web Programming, Cybersecurity, Algorithms}}
\end{itemize}\vspace{-10pt}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \begin{itemize}
      \itemsep-0.5em 
       {\setlength\itemindent{10pt} \item \textbf{Languages}{\small: Java, Python, Rust, HTML, CSS, Javascript, C{+}{+}, C}}
       {\setlength\itemindent{10pt} \item \textbf{Technologies}{\small: Elasticsearch, Flask, Git, Google Cloud, VueJS, ExpressJS, MongoDB}}
\end{itemize}\vspace{-15pt}
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Toast Inc.}{Boston, MA}
      {Software Engineering Intern}{May 2018 - Present}
      \resumeItemListStart
        \resumeItem
          {Improved testability and increased test coverage of core Android app authentication service by refactoring some of its original design and testing changes using Mockito and JUnit }
        \resumeItem
        {Designed, developed, and presented an improved solution for adding new languages as options for printer receipts on a Java web application and interfaced it with both the android app and printer hardware.}
        \resumeItem
          {Reimplemented indexing strategy for an internal microservice used to query device metrics from Elasticsearch.}
        \resumeItem
          {Streamlined app modularization process by refactoring the workflow of android device monitoring.}

      \resumeItemListEnd

    \resumeSubheading
      {Symphony Ventures}{Boston, MA}
      {Research Analyst Intern}{July 2017 - August 2017}
      \resumeItemListStart
        \resumeItem
          {Analyzed and researched more than 30 internal projects, conducting quantitative analysis on financial metrics regarding Robotic Process Automation projects for companies in the Fortune 500.}
        \resumeItem
          {Traveled to UK and Poland offices for two weeks in order to conduct interviews with consultants in order to perform in-depth analysis past projects.}
         \resumeItem
          {
            Delivered findings and collateral to a major business partner 
          }
      \resumeItemListEnd


    \resumeSubheading
      {Tufts University}{Medford, MA}
      {Teaching Assistant}{January 2017 - Present}
      \resumeItemListStart
        \resumeItem
          {Hold weekly labs for \textasciitilde300 students to reinforce concepts taught in Introduction to Computer Science(COMP11) and Data Structures(COMP15).}
        \resumeItem
          {Grade homework assignments and exams while providing personal feedback to students to improve their programming skills.}
          
      \resumeItemListEnd


  \resumeSubHeadingListEnd




%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \projectSubheading
      {Chip-8 Emulator}{Rust}{March 2018 - May 2018}
      \resumeItemListStart
        \resumeItem
          {An implementation of an emulator for the Chip-8 virtual machine built with Rust and SDL2.}
      \resumeItemListEnd

    \projectSubheading
      {Schnapz}{Javascript}{March 2018 - May 2018}
      \resumeItemListStart
        \resumeItem
          {A web application that uses two third party APIs to provide a list of recipes that can be made from based on food-based images that are uploaded to the application.}
      \resumeItemListEnd
    \projectSubheading
      {Speechy}{Python}{August 2017}
      \resumeItemListStart
        \resumeItem
          {A terminal-based program that uses Google’s Speech API and one other third party API to transcribe audio files and punctuate the transcription with approximately 90\% accuracy.}
  
      \resumeItemListEnd

    \projectSubheading
      {Arith}{C}{October 2017}
      \resumeItemListStart
        \resumeItem
          {A command-line based program that implements a lossy compression algorithm to decrease the size of images}
        \resumeItem
          {Compressing and decompressing the same image results in 97 – 99\% data retention.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Extracurriculars-----------------
\section{Extracurriculars}
\resumeSubHeadingListStart
  \resumeSubheading
    {Tufts TURBO}{Medford, MA}
      {President}{September 2017 - Present}
      \resumeItemListStart
        \resumeItem
          {Plan and host annual breakdancing competition (Turbomania) for over 300 dancers from the Greater Boston Area.}
      \resumeItemListEnd

\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
